### 2021-09-21 sections/signal_background_modeling.tex
updating the paper draft V0.1

Signal and most background processes are modelled using Monte Carlo (MC) simulation.
After the event preselection, the main background is $\ttbar$ production, often in association with jets, denoted by $\ttbar$+jets in the following.
Small contributions arise from single-top-quark, $W/Z$+jets, multijet and diboson ($WW,WZ,ZZ$) production, as well as from the associated 
production of a vector boson $V$ ($V=W,Z$) or a Higgs boson and a $\ttbar$ pair ($\ttbar V$ and $\ttbar H$). All backgrounds 
with prompt leptons, i.e.\ those originating from the decay of a $W$ boson, a $Z$ boson, or a $\tau$-lepton,
are estimated using samples of simulated events and initially normalised to their theoretical cross sections.
In the simulation, the top-quark and SM Higgs boson masses are set to $172.5~\gev$ and $125~\gev$, respectively,
and the Higgs boson is allowed to decay into all SM particles with branching ratios calculated using \textsc{Hdecay}~\cite{Djouadi:1997yw}.  
Backgrounds with non-prompt electrons or muons, with photons or jets misidentified as electrons, or with jets misidentified as $\had$ candidates, 
generically referred to as fake leptons, are estimated using data-driven methods. 
The background prediction is further improved during the statistical analysis by performing a likelihood 
fit to data using several signal-depleted analysis regions, as discussed in Sections~\ref{sec:strategy_Htautau}.

@@

Samples of simulated $\ttbar \to WbHq$ events were generated with the next-to-leading-order (NLO) generator\footnote{In the following, 
the order of a generator should be understood as referring to the order in the strong coupling constant at which the matrix-element calculation 
is performed.} {\powheg}~v2 \cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd}
%{\amcatnlolong}~2.4.3~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo})
with the NNPDF3.0 NLO~\cite{Ball:2014uwa} parton distribution function (PDF) set and interfaced to {\pythia} 8.212~\cite{Sjostrand:2007gs} with the NNPDF2.3 LO~\cite{Ball:2012cx} PDF set for the modelling of parton showering, hadronisation, and the underlying event. 
The A14~\cite{ATLASUETune4} set of tuned parameters in {\pythia} controlling the description of multiparton interactions and  
initial- and final-state radiation, referred to as the tune, was used.
The signal sample is normalised to the same total cross section as used for the inclusive $t\bar{t}\to WbWb$ sample (see discussion below) and
assuming an arbitrary branching ratio of $\BR_{\mathrm{ref}}(t\to Hq)=0.2\%$.
The case of both top quarks decaying into $Hq$ is neglected in the analysis given the existing upper limits on $\BR(t \to Hq)$ (Section~\ref{sec:intro}).

The $tH$ signal events were generated by {\amcatnlolong}~2.6.2~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo})
with the NNPDF3.0 NLO parton distribution function (PDF) set and interfaced to {\pythia} 8.212 with the NNPDF2.3 LO PDF set for the modelling of parton showering,
hadronisation, and the underlying event with the A14 tune.
Depending on either up quark or charm quark involved in the FCNC decay, the effective Lagrangian of $tqH$ interaction are parametrised using
dim-6 operators~\cite{fcnc_production_theory}. We obtain $\sigma(ug\to tH)$ = 1.4218 pb and $\sigma(cg\to tH)$ = 0.206 pb using $\BR_{\mathrm{ref}}(t\to Hq)=0.2\%$ as benchmark.

@@

Samples of $\ttbar V$ and $\ttbar H$ events were generated with {\amcatnlo}~2.2.1, using NLO matrix elements and the NNPDF3.0 NLO PDF set,
and interfaced to {\pythia}~8.210 with the NNPDF2.3 LO PDF set and the A14 tune. 
Instead, the $\ttbar V$ samples used in the $\Hbb$ search are based on LO matrix elements computed for up to two additional partons 
using the NNPDF3.0 NLO PDF set, and merged using the CKKW-L approach~\cite{Lonnblad:2001iq}.
The $\ttbar V$ samples are normalised to the NLO cross section computed with {\amcatnlo}, while the $\ttbar H$ sample is normalised using 
the NLO cross section recommended in Ref.~\cite{deFlorian:2016spz}.

@@

\subsubsection{Fake electrons and muons}
Electrons and muons only appear in the leptonic channels where there is exactly one electron or muon and at least one $\had$. Since the fake rate of $\had$ candidate is much larger than electron or muon. So in the majority of the fake lepton events, the $\had$ candidate is misidentified and the electron or muon is real, which is also proved by monte carlo studies. However the multi-jet background has large event rate and can contribute with both electron or muon and $\had$ faked, espcially to $t_l\had$ where the fake-lepton dominates and the jet multiplicity is low.  This kind of event is modelled by data-driven ABCD method by cutting on $\met$ and the lepton isolation, which is widely used in ATLAS physics analyses.

@@

\subsubsection{Fake $\tau$-lepton candidates}
\label{sec:faketaus}
The background with one or more fake $\had$ candidates mainly arises from $\ttbar$ or
multijet production, depending on the search channel.
Studies based on the simulation show that, for all the above processes, fake $\had$ candidates primarily result from the
misidentification of light-quark jets, with the contribution from $b$-quarks and gluon jets playing a subdominant role.
It is also found that the fake rate decreases for all jet flavours as the $\had$ candidate $\pt$ increases.

In the leptonic channels, the events with real electron or muon and fake taus are modelled by calibrated monte carlo with scale factors
derived from the dedicated $t\bar t$
control regions ($CR_{tt}$) using the SM $t\bar t$ decay of dilepton events and semileptonically double-btagged lepton-jet events, summarized in Table~\ref{tab:srcr},
aimed at fake taus from different origins. There are four kinds of fake taus that need to be calibrated: Type1) $\tau_{W}$'s with the opposite charge to the lepton;
Type2) $\tau_{W}$'s with the same charge as the lepton; Type 3) the fake taus from b-jets; Type4) the fake taus from other origins (mainly radiations).
These control regions are similar to the signal regions but with an additional b-jet or lepton defined as:
$t_lt_l1b\thad$, $t_lt_l2b\thad$, $t_lt_h2b\thad$-2jSS, $t_lt_h2b\thad$-2jOS, $t_lt_h2b\thad$-3jSS, and $t_lt_h2b\thad$-3jOS.
Where di-lepton regions ($t_lt_l1b\thad$ and $t_lt_l2b\thad$) are used to calibrate the Type3 and Type4 fake taus. The regions of
$t_lt_h2b\thad$-2jOS and $t_lt_h2b\thad$-3jOS are used to calibrate Type1 fake taus. Similarly for the Type2, the regions of $t_lt_h2b\thad$-2jSS and $t_lt_h2b\thad$-3jSS are used.
A simultaneous fit to data is made to derive the scale factors for the fake taus, which consists of total 24 parameters including 3 $\pt$ bins (25-35, 35-45, 45-)GeV for 1 and 3
prong taus separately. The values of these scale factors range from 0.3 to 1.28 and are applied to the corresponding signal regions with single b-tagged jet.
In $t_l\thadhad$ channel, both taus can be fake, so the calibration is applied to each tau separately, following the same procedure as $\tlhad$ channels using the
lepton and fake tau charges, then the scale factors are multiplied together. The nominal value of the scale factors will vary along with other uncertainties from
combined preformace (CP) recommendations and theory uncertainties in the final fit.
%In the control regions with single lepton, $\met > 20$GeV and at least 2 light jets and 2 b-tagged jets are required to ensure that QCD contribution is negligible.
%The calibration is done depending on different source of the fake taus and \pt. The calibration factor are derived in the dedicated
%control regions discussed in Section~\ref{sec:strategy_Htautau}.

In the hadronic channels, this background is estimated partially from data by defining control regions (CR) enriched in fake $\had$
candidates via loosened $\had$ requirements with proper fake factors and partially from monte carlo.
These CRs do not overlap with the main search regions (SRs), discussed in Section~\ref{sec:strategy_Htautau}.
The CR selection requirements are analogous to those used to define the different SRs, except
that the trailing $\had$ candidate is required to fail the medium $\had$ identification.
The events with fake trailing $\had$ candidate can be calculated by rescaling the templates of fake taus in the Fake-CR with proper fake factors (FF).
The templates are aquired by subtracting all MC background contributions with real sub-leading taus from data. The FFs are computed as
the ratio of the Data$-$MC$_\mathrm{real~tau}$ yields passing the medium tau ID to which failing the medium tau ID from different control regions and
the differences are treated as part of systematics.

>>>>

Signal and most background processes are modelled using Monte Carlo (MC) simulation.
After the event preselection, the main background is $\ttbar$ production, often in association with jets, denoted by $\ttbar$+jets in the following.
Small contributions arise from single-top-quark, $W/Z$+jets, multijet and diboson ($WW,WZ,ZZ$) production, as well as from the associated 
production of a vector boson $V$ ($V=W,Z$) or a Higgs boson and a $\ttbar$ pair ($\ttbar V$ and $\ttbar H$). All backgrounds 
with prompt leptons, i.e.\ those originating from the decay of a $W$ boson, a $Z$ boson, or a $\tau$-lepton,
are estimated using samples of simulated events and initially normalised to their theoretical cross sections.
In the simulation, the top-quark and SM Higgs boson masses are set to $172.5~\gev$ and $125~\gev$, respectively,
and the Higgs boson is forced to decay into $H\to \tau\tau$ with branching ratio calculated using \textsc{Hdecay}~\cite{Djouadi:1997yw}.  
Backgrounds with non-prompt electrons or muons, with photons or jets misidentified as electrons, or with jets misidentified as $\had$ candidates, 
generically referred to as fake leptons, are estimated using data-driven methods. 
The background prediction is further improved during the statistical analysis by performing a likelihood 
fit to data using several signal-depleted analysis regions, as discussed in Sections~\ref{sec:strategy_Htautau}.

@@

Samples of simulated $\ttbar \to WbHq$ events were generated with the next-to-leading-order (NLO) generator\footnote{In the following, 
the order of a generator should be understood as referring to the order in the strong coupling constant at which the matrix-element calculation 
is performed.} {\powheg}~v2 \cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd}
%{\amcatnlolong}~2.4.3~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo})
with the NNPDF3.0 NLO~\cite{Ball:2014uwa} parton distribution function (PDF) set and interfaced to {\pythia} 8.212~\cite{Sjostrand:2007gs} with the NNPDF2.3 LO~\cite{Ball:2012cx} PDF set for the modelling of parton showering, hadronisation, and the underlying event. 
The A14~\cite{ATLASUETune4} set of tuned parameters in {\pythia} controlling the description of multiparton interactions and  
initial- and final-state radiation, referred to as the tune, was used.
The signal sample is normalised to the same total cross section as used for the inclusive $t\bar{t}\to WbWb$ sample (see discussion below) and
assuming an arbitrary branching ratio of $\BR_{\mathrm{ref}}(t\to Hq)=0.1\%$.
The case of both top quarks decaying into $Hq$ is neglected in the analysis given the existing upper limits on $\BR(t \to Hq)$ (Section~\ref{sec:intro}).

The $tH$ signal events were generated by {\amcatnlolong}~2.6.2~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo})
with the NNPDF3.0 NLO parton distribution function (PDF) set and interfaced to {\pythia} 8.212 with the NNPDF2.3 LO PDF set for the modelling of parton showering,
hadronisation, and the underlying event with the A14 tune.
Depending on either up quark or charm quark involved in the FCNC production, the effective Lagrangian of $tqH$ interaction are parametrised using
dim-6 operators~\cite{fcnc_production_theory}. We obtain $\sigma(ug\to tH)$ = 0.711 pb and $\sigma(cg\to tH)$ = 0.103 pb using $\BR_{\mathrm{ref}}(t\to Hq)=0.1\%$ as benchmark.

@@

Samples of $\ttbar V$ and $\ttbar H$ events were generated with {\amcatnlo}~2.2.1, using NLO matrix elements and the NNPDF3.0 NLO PDF set,
and interfaced to {\pythia}~8.210 with the NNPDF2.3 LO PDF set and the A14 tune. 
%Instead, the $\ttbar V$ samples used in the $\Hbb$ search are based on LO matrix elements computed for up to two additional partons 
%using the NNPDF3.0 NLO PDF set, and merged using the CKKW-L approach~\cite{Lonnblad:2001iq}.
The $\ttbar V$ samples are normalised to the NLO cross section computed with {\amcatnlo}, while the $\ttbar H$ sample is normalised using 
the NLO cross section recommended in Ref.~\cite{deFlorian:2016spz}.

@@

\subsubsection{Fake electrons and muons}
Electrons and muons only appear in the leptonic channels where there is exactly one electron or muon and at least one $\had$. Since the fake rate of $\had$ candidate is much larger than electron or muon. So in the majority of the fake lepton events, the $\had$ candidate is misidentified and the electron or muon is real, which is also proved by monte carlo studies. However the multi-jet background has large event rate and can contribute with both electron or muon and $\had$ faked, espcially to $t_l\had$ where the fake-lepton dominates.
%and the jet multiplicity is low.
This kind of event is modelled by data-driven ABCD method by cutting on $\met$ and the tight lepton isolation using PLIV, which is widely used in ATLAS physics analyses.

@@

\subsubsection{Fake $\tau$-lepton candidates}
\label{sec:faketaus}
The background with one or more fake $\had$ candidates mainly arises from $\ttbar$ or
multijet production, depending on the search channels.
Studies based on the simulation show that, for all the above processes, fake $\had$ candidates primarily result from the
misidentification of light-quark jets, with the contribution from $b$-quarks and gluon jets playing a subdominant role.
It is also found that the fake rate decreases for all jet flavours as the $\had$ candidate $\pt$ increases.

In the leptonic channels, the events with real electron or muon and fake taus are modelled by calibrating monte carlo with scale factors
derived from the dedicated $t\bar t$
control regions ($CR_{tt}$) using the SM $t\bar t$ decay of dilepton events and semileptonically double-btagged lepton-jet events, summarized in Table~\ref{tab:srcr},
aimed at fake taus from different origins. There are four kinds of fake taus that need to be calibrated: Type1) the fake taus from $W$-jets ($\tau_{W}$)
with the opposite charge to the lepton;
Type2) $\tau_{W}$'s with the same charge as the lepton; Type 3) the fake taus from $b$-jets; Type4) the fake taus from other origins (mainly radiations).
These control regions are similar to the signal regions but with an addition $b$-jet or lepton defined as following:
$t_lt_l1b\thad$, $t_lt_l2b\thad$, $t_lt_h2b\thad$-2jSS, $t_lt_h2b\thad$-2jOS, $t_lt_h2b\thad$-3jSS, and $t_lt_h2b\thad$-3jOS.
The di-lepton regions ($t_lt_l1b\thad$ and $t_lt_l2b\thad$) are used to calibrate the Type3 and Type4 fake taus. The regions of
$t_lt_h2b\thad$-2jOS and $t_lt_h2b\thad$-3jOS are used to calibrate Type1 fake taus.
Similarly for the Type2, the regions of $t_lt_h2b\thad$-2jSS and $t_lt_h2b\thad$-3jSS are used.
A simultaneous fit to data is made to derive the scale factors for the fake taus in MC, which consist of total 24 parameters
including four types, 3 $\pt$ bins (25-35, 35-45, 45- GeV), 2 bins for 1 and 3 prong taus separately.
The values of these scale factors range from 0.3 to 1.28 and are applied to the corresponding signal regions with single b-tagged jet.

In the $t_l\thadhad$ channel, both taus can be fake, so the calibration is applied to each tau separately, following the same procedure as $\tlhad$ channels using the
lepton and fake tau charges, then the scale factors are multiplied together. The nominal value of the scale factors will vary along with other uncertainties from
combined preformace (CP) recommendations and theory uncertainties in the final fit.
%In the control regions with single lepton, $\met > 20$GeV and at least 2 light jets and 2 b-tagged jets are required to ensure that QCD contribution is negligible.
%The calibration is done depending on different source of the fake taus and \pt. The calibration factor are derived in the dedicated
%control regions discussed in Section~\ref{sec:strategy_Htautau}.

In the hadronic channels, this background is estimated partially from data by defining control regions (CR) enriched in fake $\had$
candidates via loosened $\had$ requirements with proper fake factors and partially from monte carlo~\cite{ATLAS-CONF-2021-044}.
These CRs do not overlap with the main search regions (SRs), discussed in Section~\ref{sec:strategy_Htautau}.
The CR selection requirements are analogous to those used to define the different SRs, except
that the trailing $\had$ candidate is required to fail the medium $\had$ identification.
The events with fake trailing $\had$ candidate can be calculated by rescaling the templates of fake taus in the Fake-CR with proper fake factors (FF).
The templates are aquired by subtracting all MC background contributions with real sub-leading taus from data. The FFs are computed as
the ratio of the Data$-$MC$_\mathrm{real~tau}$ yields passing the medium tau ID to which failing the medium tau ID from different control regions and
the differences are treated as part of systematics.

### 2021-09-21 sections/statistical_analysis.tex
updating the paper draft V0.1

The final discriminant distributions across all analysis regions considered are jointly analysed to test for the 
presence of a signal. The statistical analysis uses a binned likelihood function ${\cal L}(\mu,\theta)$ constructed as
a product of Poisson probability terms over all bins considered in the search. This function depends
on the signal-strength parameter $\mu$, defined as a factor multiplying the expected yield of $\Hq$ signal events
normalised to a reference branching ratio $\BR_{\mathrm{ref}}(t\to Hq)=0.2\%$,
and $\theta$, a set of nuisance parameters that encode the effect of systematic uncertainties on the signal and background expectations. 
Therefore, the expected total number of events in a given bin depends on $\mu$ and $\theta$. 
All nuisance parameters are subject to Gaussian constraints in the likelihood.
For a given value of $\mu$, the nuisance parameters $\theta$ allow variations of the expectations for signal and background
according to the corresponding systematic uncertainties, and their fitted values result in the deviations from
the nominal expectations that globally provide the best fit to the data.
This procedure allows a reduction of the impact of systematic uncertainties on 
the search sensitivity by taking advantage of the highly populated background-dominated bins included in the likelihood fit.
%To verify the improved background prediction, fits under the background-only hypothesis are performed, 
%and differences between the data and the post-fit background prediction are checked 
%using kinematic variables other than the ones used in the fit. 
Statistical uncertainties in each bin of the predicted final discriminant distributions are taken into account by dedicated parameters in the fit.     
The best-fit $\BR(t\to Hq)$ is obtained by performing a binned likelihood fit to the data under the signal-plus-background
hypothesis, maximising the likelihood function ${\cal L}(\mu,\theta)$ over $\mu$ and $\theta$.

The fitting procedure was initially validated through extensive studies using mock data, defined as the sum of all predicted backgrounds 
plus an injected signal of variable strength, as well as by performing fits to real data where bins of the final discriminant variable with 
a signal contamination above 5\% are excluded (referred to as blinding requirements).
In both cases, the robustness of the model for systematic uncertainties is established by verifying the stability of the fitted background 
when varying assumptions about some of the leading sources of uncertainty. 
After this, the blinding requirements
are removed in the data and a fit under the signal-plus-background hypothesis is performed. Further checks involve the comparison of the fitted 
nuisance parameters before and after removal of the blinding requirements, and their values are found to be consistent. In addition, it is verified that the 
fit is able to correctly determine the strength of a simulated signal injected into the real data.

The test statistic $q_\mu$ is defined as the profile likelihood ratio, 
$q_\mu = -2\ln({\cal L}(\mu,{\hat{\theta}}_\mu)/{\cal L}(\hat{\mu},\hat{\theta}))$,
where $\hat{\mu}$ and $\hat{\theta}$ are the values of the parameters that
maximise the likelihood function (subject to the constraint $0\leq \hat{\mu} \leq \mu$), and ${\hat{\theta}}_\mu$ are the values of the
nuisance parameters that maximise the likelihood function for a given value of $\mu$. 
The test statistic $q_\mu$ is evaluated with the {\textsc RooFit} package~\cite{Verkerke:2003ir,RooFitManual}.
A related statistic is used to determine whether the observed data is compatible with the background-only hypothesis (the so-called discovery test)  
by setting $\mu=0$ in the profile likelihood ratio and leaving $\hat{\mu}$ unconstrained: $q_0 = -2\ln({\cal L}(0,{\hat{\theta}}_0)/{\cal L}(\hat{\mu},\hat{\theta}))$.
The $p$-value (referred to as $p_0$), representing the level of agreement between the data and the background-only hypothesis, is estimated by integrating
%representing the probability of the data being compatible with the background-only hypothesis is estimated by integrating
%the distribution of $q_0$ obtained from background-only pseudo-experiments, approximated using the asymptotic formulae given in Refs.~\cite{Cowan:2010js}, 
the distribution of $q_0$ based on the asymptotic formulae in Ref.~\cite{Cowan:2010js}, 
above the observed value of $q_0$ in the data. 
%The observed $p_0$-value is checked for each explored signal scenario.
%In the case of the data being compatible with the background-only hypothesis, 
Upper limits on $\mu$, and thus on 
$\BR(t\to Hq)$, are derived by using $q_\mu$ in the CL$_{\textrm{s}}$ method~\cite{Junk:1999kv,Read:2002hq}.
For a given signal scenario, values of the $\BR(t\to Hq)$ yielding CL$_{\textrm{s}} < 0.05$, 
where CL$_{\textrm{s}}$ is computed using the asymptotic approximation~\cite{Cowan:2010js}, are excluded at $\geq 95\%$ CL.

>>>>

The final discriminant distributions across all analysis regions considered are jointly analysed to test for the 
presence of a signal. The statistical analysis uses a binned likelihood function ${\cal L}(\mu,\theta)$ constructed as
a product of Poisson probability terms over all bins considered in the search. This function depends
on the signal-strength parameter $\mu$, defined as a factor multiplying the expected yield of $tH$ and $tt(Hq)$ signal events
normalised to a reference branching ratio $\BR_{\mathrm{ref}}(t\to Hq)=0.1\%$,
and $\theta$, a set of nuisance parameters that encode the effect of systematic uncertainties on the signal and background expectations. 
Therefore, the expected total number of events in a given bin depends on $\mu$ and $\theta$. 
All nuisance parameters are subject to Gaussian constraints in the likelihood.
For a given value of $\mu$, the nuisance parameters $\theta$ allow variations of the expectations for signal and background
according to the corresponding systematic uncertainties, and their fitted values result in the deviations from
the nominal expectations that globally provide the best fit to the data.
This procedure allows a reduction of the impact of systematic uncertainties on 
the search sensitivity by taking advantage of the highly populated background-dominated bins included in the likelihood fit.
%To verify the improved background prediction, fits under the background-only hypothesis are performed, 
%and differences between the data and the post-fit background prediction are checked 
%using kinematic variables other than the ones used in the fit. 
Statistical uncertainties in each bin of the predicted final discriminant distributions are taken into account by dedicated parameters in the fit.     
The best-fit $\BR(t\to Hq)$ is obtained by performing a binned likelihood fit to the data under the signal-plus-background
hypothesis, maximising the likelihood function ${\cal L}(\mu,\theta)$ over $\mu$ and $\theta$.

The fitting procedure was initially validated through extensive studies using mock data, defined as the sum of all predicted backgrounds 
plus an injected signal of variable strength, as well as by performing fits to real data where bins of the final discriminant variable with 
a signal contamination above 10\% are excluded (referred to as blinding requirements).
In both cases, the robustness of the model for systematic uncertainties is established by verifying the stability of the fitted background 
when varying assumptions about some of the leading sources of uncertainty. 
After this, the blinding requirements
are removed in the data and a fit under the signal-plus-background hypothesis is performed. Further checks involve the comparison of the fitted 
nuisance parameters before and after removal of the blinding requirements, and their values are found to be consistent. In addition, it is verified that the 
fit is able to correctly determine the strength of a simulated signal injected into the real data.

The test statistic $q_\mu$ is defined as the profile likelihood ratio, 
$q_\mu = -2\ln({\cal L}(\mu,{\hat{\theta}}_\mu)/{\cal L}(\hat{\mu},\hat{\theta}))$,
where $\hat{\mu}$ and $\hat{\theta}$ are the values of the parameters that
maximise the likelihood function (subject to the constraint $0\leq \hat{\mu} \leq \mu$), and ${\hat{\theta}}_\mu$ are the values of the
nuisance parameters that maximise the likelihood function for a given value of $\mu$. 
The test statistic $q_\mu$ is evaluated with the {\textsc RooFit} package~\cite{Verkerke:2003ir,RooFitManual}.
%A related statistic is used to determine whether the observed data is compatible with the background-only hypothesis (the so-called discovery test)  
%by setting $\mu=0$ in the profile likelihood ratio and leaving $\hat{\mu}$ unconstrained: $q_0 = -2\ln({\cal L}(0,{\hat{\theta}}_0)/{\cal L}(\hat{\mu},\hat{\theta}))$.
%The $p$-value (referred to as $p_0$), representing the level of agreement between the data and the background-only hypothesis, is estimated by integrating
%%representing the probability of the data being compatible with the background-only hypothesis is estimated by integrating
%%the distribution of $q_0$ obtained from background-only pseudo-experiments, approximated using the asymptotic formulae given in Refs.~\cite{Cowan:2010js}, 
%the distribution of $q_0$ based on the asymptotic formulae in Ref.~\cite{Cowan:2010js}, 
%above the observed value of $q_0$ in the data. 
%%The observed $p_0$-value is checked for each explored signal scenario.
%%In the case of the data being compatible with the background-only hypothesis, 
%Upper limits on $\mu$, and thus on 
%$\BR(t\to Hq)$, are derived by using $q_\mu$ in the CL$_{\textrm{s}}$ method~\cite{Junk:1999kv,Read:2002hq}.
%For a given signal scenario, values of the $\BR(t\to Hq)$ yielding CL$_{\textrm{s}} < 0.05$, 
%where CL$_{\textrm{s}}$ is computed using the asymptotic approximation~\cite{Cowan:2010js}, are excluded at $\geq 95\%$ CL.

In the absence of signal, exclusion limits are set on $\mu$ , and thus on
$\BR(t\to Hq)$, are derived by using $q_\mu$ in the CL$_{\textrm{s}}$ method~\cite{Junk:1999kv,Read:2002hq}.
For a given signal scenario, values of the $\BR(t\to Hq)$ yielding CL$_{\textrm{s}} < 0.05$,
where CL$_{\textrm{s}}$ is computed using the asymptotic approximation~\cite{Cowan:2010js}, are excluded at $\geq 95\%$ CL.
